\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-22 main.Rmd
code tweaks

As a data restructuring tool, the interactivity of calendar-based display can be easily enabled, as long as the interactive graphic system remains true to the spirit of the grammar of graphics, for example **plotly** [@plotly] in R. As a standalone display, an interactive tooltip can be added to show labels when mousing over it in the calendar layout, for example the hourly count with the time of day. It is difficult to sense the values from the static display, but the tooltip makes it possible. Options in function `frame_calendar` can be ported to a form of selection button or text input in a graphical user interface like shiny \ref{XXX}. The display will update on the fly accordingly via clicking or text input, as desired.

Linking calendar displays to other types of charts is valuable to visually explore the relationships between variables. An example can be found in \ref{YYY}. The calendar most naturally serves as a tool for date selection: by selecting and brushing the glyphs in the calendar, it subsequently highlights the elements of corresponding dates in other time-based plots. Conversely, selecting on weather data plots, linked to the calendar can help to assess if very hot/cold days and heavy rain affect the number of people walking in downtown Melbourne. The linking between weather data and calendar display is achieved using the common dates.

@@

Figure \ref{fig:hod} shows energy consumption against time of day, separately by week day and weekend. Household 1 is an early bird, starting their day before 6 and going back home around 18 on week days. They switch air conditioning or heating on when they get home from work and keep it operating till mid-night, learned from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for  household 2 indicates that perhaps air conditioning or heating runs continuously for some periods, consuming the twice the energy as household 1. A third peak occurs around 3pm for household 3 only, likely when the kids are home from school. They also have a consistent energy pattern between week days and weekends. As for household 4, their home routine starts after 6pm on week days. Figures \ref{fig:dow} and \ref{fig:hod}, part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households.

```{r hod, fig.height = 6, fig.cap = "Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting week days and weekends for each household. All have different daily routines between week days and weekends, except for household 3. On week days, household 1 wakes up early before 6am, and household 2 around 6am, followed by household 3 and 4. The use of air conditioning and heating are noted in household 1 and 2."}
```

Figure \ref{fig:h1}, \ref{fig:h2}, \ref{fig:h3} and \ref{fig:h4} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing over household 1, you can see that their overall energy use is low. Their week day energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months in the evening and weekends. In household 2, heating keeps functioning for consecutive hours, which is evident in the mid July; while household 1 uses heating cautiously. These observations help to explain the stripes and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous plots. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h3} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.
# Discussion
\label{sec:discussion}

@@

```{r write-bib}
write_bib(c("ggplot2", "tidyverse", "sugrrants", "geofacet", .packages()), 'packages.bib')
```

>>>>

As a data restructuring tool, the interactivity of calendar-based display can be easily enabled, as long as the interactive graphic system remains true to the spirit of the grammar of graphics, for example **plotly** [@plotly] in R. As a standalone display, an interactive tooltip can be added to show labels when mousing over it in the calendar layout, for example the hourly count with the time of day. It is difficult to sense the values from the static display, but the tooltip makes it possible. Options in function `frame_calendar` can be ported to a form of selection button or text input in a graphical user interface like R shiny [@R-shiny]. The display will update on the fly accordingly via clicking or text input, as desired.

Linking calendar displays to other types of charts is valuable to visually explore the relationships between variables. An example can be found in the **wanderer4melb** shiny application [@R-wanderer4melb]. The calendar most naturally serves as a tool for date selection: by selecting and brushing the glyphs in the calendar, it subsequently highlights the elements of corresponding dates in other time-based plots. Conversely, selecting on weather data plots, linked to the calendar can help to assess if very hot/cold days and heavy rain affect the number of people walking in downtown Melbourne. The linking between weather data and calendar display is achieved using the common dates.

@@

Figure \ref{fig:hod} shows energy consumption against time of day, separately by week day and weekend. Household 1 is an early bird, starting their day before 6 and going back home around 18 on week days. They switch air conditioning or heating on when they get home from work and keep it operating till mid-night, learned from the small horizontal cluster of points around 0.8 kWh. On the other hand, the stripes above 1 kWh for  household 2 indicates that perhaps air conditioning or heating runs continuously for some periods, consuming the twice the energy as household 1. A third peak occurs around 3pm for household 3 only, likely when the kids are home from school. They also have a consistent energy pattern between week days and weekends. As for household 4, their home routine starts after 18 on week days. Figures \ref{fig:dow} and \ref{fig:hod}, part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households.

```{r hod, fig.height = 6, fig.cap = "Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting week days and weekends for each household. All have different daily routines between week days and weekends, except for household 3. On week days, household 1 wakes up early before 6, and household 2 around 6, followed by household 3 and 4. The use of air conditioning and heating are noted in household 1 and 2."}
```

Figure \ref{fig:h1}, \ref{fig:h2}, \ref{fig:h3} and \ref{fig:h4} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing over household 1, you can see that their overall energy use is low. Their week day energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months in the evening and weekends. In household 2, heating keeps functioning for consecutive hours, which is evident in the mid July; while household 1 uses heating cautiously. These observations help to explain the stripes and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous plots. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h3} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

# Discussion
\label{sec:discussion}

@@

```{r write-bib}
write_bib(c("ggplot2", "tidyverse", "sugrrants", "geofacet", "shiny", .packages()), 'packages.bib')
```

### 2018-10-22 main.tex
code tweaks

\subsubsection{Interactivity}\label{interactivity}

As a data restructuring tool, the interactivity of calendar-based
display can be easily enabled, as long as the interactive graphic system
remains true to the spirit of the grammar of graphics, for example
\textbf{plotly} \citep{plotly} in R. As a standalone display, an
interactive tooltip can be added to show labels when mousing over it in
the calendar layout, for example the hourly count with the time of day.
It is difficult to sense the values from the static display, but the
tooltip makes it possible. Options in function \texttt{frame\_calendar}
can be ported to a form of selection button or text input in a graphical
user interface like shiny \ref{XXX}. The display will update on the fly
accordingly via clicking or text input, as desired.

Linking calendar displays to other types of charts is valuable to
visually explore the relationships between variables. An example can be
found in \ref{YYY}. The calendar most naturally serves as a tool for
date selection: by selecting and brushing the glyphs in the calendar, it
subsequently highlights the elements of corresponding dates in other
time-based plots. Conversely, selecting on weather data plots, linked to
te calendar can help to assess if very hot/cold days and heavy rain
affect the number of people walking in downtown Melbourne. The linking
between weather data and calendar display is achieved using the common
dates.

\section{Case study}\label{case-study}

@@

Figure \ref{fig:hod} shows energy consumption against time of day,
separately by week day and weekend. Household 1 is an early bird,
starting their day before 6 and going back home around 18 on week days.
They switch air conditioning or heating on when they get home from work
and keep it operating till mid-night, learned from the small horizontal
cluster of points around 0.8 kWh. On the other hand, the stripes above 1
kWh for household 2 indicates that perhaps air conditioning or heating
runs continuously for some periods, consuming the twice the energy as
household 1. A third peak occurs around 3pm for household 3 only, likely
when the kids are home from school. They also have a consistent energy
pattern between week days and weekends. As for household 4, their home
routine starts after 6pm on week days. Figures \ref{fig:dow} and
\ref{fig:hod}, part of a traditional graphical toolkit, are useful for
summarizing overall deviations across days and households.

@@

\caption{Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting week days and weekends for each household. All have different daily routines between week days and weekends, except for household 3. On week days, household 1 wakes up early before 6am, and household 2 around 6am, followed by household 3 and 4. The use of air conditioning and heating are noted in household 1 and 2.}\label{fig:hod}
\end{figure}

Figure \ref{fig:h1}, \ref{fig:h2}, \ref{fig:h3} and \ref{fig:h4} display
the data in calendar layout individually for each household, unfolding
their day-to-day life. Glancing over household 1, you can see that their
overall energy use is low. Their week day energy use is distinguishable
from their weekends, indicating a working household. The air conditioner
appears to be used in the summer months in the evening and weekends. In
household 2, heating keeps functioning for consecutive hours, which is
evident in the mid July; while household 1 uses heating cautiously.
These observations help to explain the stripes and clusters in Figure
\ref{fig:hod}. The calendar plots speak the stories about vacation time
that are untold by previous plots. Household 1 is on vacation over three
weeks of June, and household 2 was also away for holidays during
Christmas and the second week of June. Figure \ref{fig:h3} shows
household 3 takes two one-month-long family trips in September till
early October and in June/July, and household 4 is away over two or
three weeks in early October, December and late June. The use of air
conditioning and heating leaves no trace in these two households. \#
Discussion \label{sec:discussion}

@@

\section*{Acknowledgements}\label{acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

>>>>

\hypertarget{interactivity}{%
\subsubsection{Interactivity}\label{interactivity}}

As a data restructuring tool, the interactivity of calendar-based
display can be easily enabled, as long as the interactive graphic system
remains true to the spirit of the grammar of graphics, for example
\textbf{plotly} \citep{plotly} in R. As a standalone display, an
interactive tooltip can be added to show labels when mousing over it in
the calendar layout, for example the hourly count with the time of day.
It is difficult to sense the values from the static display, but the
tooltip makes it possible. Options in function \texttt{frame\_calendar}
can be ported to a form of selection button or text input in a graphical
user interface like R shiny \citep{R-shiny}. The display will update on
the fly accordingly via clicking or text input, as desired.

Linking calendar displays to other types of charts is valuable to
visually explore the relationships between variables. An example can be
found in the \textbf{wanderer4melb} shiny application
\citep{R-wanderer4melb}. The calendar most naturally serves as a tool
for date selection: by selecting and brushing the glyphs in the
calendar, it subsequently highlights the elements of corresponding dates
in other time-based plots. Conversely, selecting on weather data plots,
linked to the calendar can help to assess if very hot/cold days and
heavy rain affect the number of people walking in downtown Melbourne.
The linking between weather data and calendar display is achieved using
the common dates.

\hypertarget{case-study}{%
\section{Case study}\label{case-study}}

@@

Figure \ref{fig:hod} shows energy consumption against time of day,
separately by week day and weekend. Household 1 is an early bird,
starting their day before 6 and going back home around 18 on week days.
They switch air conditioning or heating on when they get home from work
and keep it operating till mid-night, learned from the small horizontal
cluster of points around 0.8 kWh. On the other hand, the stripes above 1
kWh for household 2 indicates that perhaps air conditioning or heating
runs continuously for some periods, consuming the twice the energy as
household 1. A third peak occurs around 3pm for household 3 only, likely
when the kids are home from school. They also have a consistent energy
pattern between week days and weekends. As for household 4, their home
routine starts after 18 on week days. Figures \ref{fig:dow} and
\ref{fig:hod}, part of a traditional graphical toolkit, are useful for
summarizing overall deviations across days and households.

@@

\caption{Scatterplot between half-hourly energy usage and time of day with the averages overlaid, constrasting week days and weekends for each household. All have different daily routines between week days and weekends, except for household 3. On week days, household 1 wakes up early before 6, and household 2 around 6, followed by household 3 and 4. The use of air conditioning and heating are noted in household 1 and 2.}\label{fig:hod}
\end{figure}

Figure \ref{fig:h1}, \ref{fig:h2}, \ref{fig:h3} and \ref{fig:h4} display
the data in calendar layout individually for each household, unfolding
their day-to-day life. Glancing over household 1, you can see that their
overall energy use is low. Their week day energy use is distinguishable
from their weekends, indicating a working household. The air conditioner
appears to be used in the summer months in the evening and weekends. In
household 2, heating keeps functioning for consecutive hours, which is
evident in the mid July; while household 1 uses heating cautiously.
These observations help to explain the stripes and clusters in Figure
\ref{fig:hod}. The calendar plots speak the stories about vacation time
that are untold by previous plots. Household 1 is on vacation over three
weeks of June, and household 2 was also away for holidays during
Christmas and the second week of June. Figure \ref{fig:h3} shows
household 3 takes two one-month-long family trips in September till
early October and in June/July, and household 4 is away over two or
three weeks in early October, December and late June. The use of air
conditioning and heating leaves no trace in these two households.

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\label{sec:discussion}

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}
